### 2016-06-01 papers/thesis-vischer/Thesis.tex
citation fixing, added small content to square well. NOW FINSHED. Tests skipped!

This leads us to choose $\epsilon$ and $\sigma$ as natural scales for the quantities of our simulation. We then define dimensionless temperatures $T/\epsilon$, energies $E/\epsilon$, and distances $r/\sigma$. Moreover, we make the decision to work in geometric units for coding simplicity, setting the Boltzmann constant $k_B$ to one. This then allows us to reasonably compare energies and temperatures since they have the same units.

>>>>

This leads us to choose well depth $\epsilon$ and $\sigma$ as natural scales for the quantities of our simulation. For reference, recent\cite{clarkwater} work estimates that the best square well approximation for water is a sphere radius of $\sigma = 3.03 \AA$, a well depth of $\epsilon = 21.5433 \text{m eV}$, and a range of interaction of $\lambda = 1.7889$. We then define dimensionless temperatures $T/\epsilon$, energies $E/\epsilon$, and distances $r/\sigma$. Moreover, we make the decision to work in geometric units for coding simplicity, setting the Boltzmann constant $k_B$ to one. This then allows us to reasonably compare energies and temperatures since they have the same units.
